Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-04-12 results.tex
Fixed some references and typos in table

\begin{table*}
%\begin{table*}[hbtp]
%\renewcommand{\arraystretch}{1.3}
\footnotesize
\caption{}
\begin{threeparttable} 
\begin{tabularx}{18cm}{p{3.4cm}p{0.3cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}}
\toprule
\textbf{Question} & \multicolumn{6}{c}{\textbf{Astro Hack Week}} & \multicolumn{6}{c}{\textbf{GeoHackWeek}} & \multicolumn{6}{c}{\textbf{NeuroHackWeek}} \\ \midrule
 & $N$ & $\mathrm{dof}_{\chi^2}$emph{a} & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}$ & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}$\emph{b} & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}$ & $\phi_c$ \\ \midrule
\multicolumn{16}{l}{\textbf{Comparison with career stage}}  \\ \midrule
New topics, tools, methods (a) & 61 & 10 & 5.64 & 0.85 & 1.93 & 0 & 36 & 6 & 2.51 & 0.87 & 1.88 & 0 & 41& 10 & 15.53 & 0.15 & 1.9 & 0.23 \\
Improvement of research (b) & 61 & 6 &  9.89 & 0.13 & 1.93 & 0.18 & 35 & 4 & 12.41 & 0.02 & 1.88 & 0.35 & 40 & 6 & 7.42 & 0.28 & 1.90 & 0.13 \\
Better science (c) & 59 & 6 & 3.79 & 0.70 & 1.93 & 0 & 35 & 4 & 10.61 & 0.03 & 1.88 & 0.31 & 40 & 4 &  5.06 & 0.29 & 1.90 & 0.11\\ 
Teaching (d) & 10 & 61 & 13.65 & 0.19 & 1.93 & 0.17 & 36 & 10 & 13.68 & 0.19 & 1.88 & 0.22 & 40 & 10 & 6.90 & 0.74 & 1.90 & 0 \\ \midrule
\multicolumn{16}{l}{\textbf{Gender Identity}} \\ \midrule
Improvement of research (b) & 60 & 3 & 2.08 & 0.56 & 0.98 & 0 & 35 & 2 & 5.26 & 0.07 & 0.97 & 0.30 & 40 & 3 & 7.62 & 0.05 & 0.97 & 0.34\\
Teaching (d) & 61 & 5 & 7.30 & 0.20 & 0.98 & 0.19 & 36 & 5 & 12.71 & 0.26 & 0.97 & 0.46 & 40 &5 & 3.17 & 0.67 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 3.70 & 0.45 & 0.98 & 0 & 36 & 3 & 5.89 & 0.12 & 0.97 & 0.28 & 41 & 3 & 4.42 & 0.22 & 0.98 & 0.18\\
Valued contributions (f) & 57 & 4 & 5.98 & 0.20 & 0.98 & 0.18 & 34 & 5 & 9.46 & 0.09 & 0.97 & 0.36 & 38 & 5 & 6.75 & 0.34 & 0.97 & 0.21 \\ \midrule
\multicolumn{16}{l}{\textbf{Racial/ethnic Identity}} \\ \midrule
Improvement of research (b)  & 59 & 3 & 0.97 & 0.81 & 0.98 & 0 & 34 &2 & 0.01 & 0.99 & 0.97 & 0 & 39 & 3 & 2.79 & 0.43 & 0.97 & 0 \\
Teaching (d) & 61 & 5 & 5.63 & 0.34 & 0.98 & 0.09 & 34 & 4 & 1.29 & 0.86 & 0.97 & 0 & 39 & 5 & 3.06 & 0.69 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 1.64 & 0.80 & 0.98 & 0 & 34 & 3 & 8.42 & 0.04 & 0.97 & 0.40 & 40 & 3 & 3.49 & 0.32 & 0.97 & 0.10 \\
Valued contributions (f) & 58 & 4 & 13.14 & 0.01 & 0.98 & 0.40 & 32 & 5 & 2.49 & 0.78 & 0.96 & 0 & 37 & 5 & 4.05 & 0.54 & 0.97 & 0 \\ 
\bottomrule
\end{tabularx}
   \begin{tablenotes}
      \item{Respondents to a post-event evaluation survey indicate their level of agreement on a six-point Likert-type scale to a range of statements (corresponding to Figure \ref{fig:survey}). Results are for hack weeks held in 2016 and 2017 for AHW and in 2016 for GHW and NHW, respectively. The number of respondents for each question is included in the table above. Additional figures showing the distributions of scores are available in the Supplementary Materials.}
      \item[\emph{a}]{The degrees of freedom for Cram\'{e}r's V corrected according to \citet{bergsma2013}}
      \item[\emph{b}]{While the range of Likert items was the same for every question, the degrees of freedom for $\chi^2$ and Cram'{e}r's V may differ depending on the number of items with non-zero responses, and the number of non-zero items in the independent variable.}

@@

Given the broad diversity in skills and backgrounds of participants admitted to our hack weeks, a dependence of learning outcomes and teaching on career stage is plausible. At the same time, we put forth the hypothesis earlier in the this paper that peer learning is a major mode of knowledge transfer during hack weeks, and that this type of learning takes place at all career stages. However, we find no strong evidence for a significant difference between early-career researchers and senior participants for any of the three hack weeks for questions regarding learning outcomes of new tools and topics (a), improvements in day-to-day research (b) or overall improvements in science (c) (all statistical results are presented in Table \ref{tab:survey}). Only for GHW we find an indication that early-career researchers agree more strongly that the hack week improved their day-to-day research (p=0.02) with a large effect size of $\phi_c = 0.4$ (following \citet{cohen1988}). 
Similarly, we find no strong indication that late-career researchers self-report a higher level of teaching at hack weeks compared to early-career researchers (d).

>>>>

\begin{table*}
%\begin{table*}[hbtp]
%\renewcommand{\arraystretch}{1.3}
\footnotesize
\caption{}
\begin{threeparttable} 
\begin{tabularx}{18cm}{p{3.4cm}p{0.3cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}p{0.33cm}}
\toprule
\textbf{Question} & \multicolumn{6}{c}{\textbf{Astro Hack Week}} & \multicolumn{6}{c}{\textbf{GeoHackWeek}} & \multicolumn{6}{c}{\textbf{NeuroHackWeek}} \\ \midrule
 & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ \\ \midrule
\multicolumn{16}{l}{\textbf{Comparison with career stage}}  \\ \midrule
New topics, tools, methods (a) & 61 & 10 & 5.64 & 0.85 & 1.93 & 0 & 36 & 6 & 2.51 & 0.87 & 1.88 & 0 & 41& 10 & 15.53 & 0.15 & 1.9 & 0.23 \\
Improvement of research (b) & 61 & 6 &  9.89 & 0.13 & 1.93 & 0.18 & 35 & 4 & 12.41 & 0.02 & 1.88 & 0.35 & 40 & 6 & 7.42 & 0.28 & 1.90 & 0.13 \\
Better science (c) & 59 & 6 & 3.79 & 0.70 & 1.93 & 0 & 35 & 4 & 10.61 & 0.03 & 1.88 & 0.31 & 40 & 4 &  5.06 & 0.29 & 1.90 & 0.11\\ 
Teaching (d) & 61 & 10 & 13.65 & 0.19 & 1.93 & 0.17 & 36 & 10 & 13.68 & 0.19 & 1.88 & 0.22 & 40 & 10 & 6.90 & 0.74 & 1.90 & 0 \\ \midrule
\multicolumn{16}{l}{\textbf{Gender Identity}} \\ \midrule
Improvement of research (b) & 60 & 3 & 2.08 & 0.56 & 0.98 & 0 & 35 & 2 & 5.26 & 0.07 & 0.97 & 0.30 & 40 & 3 & 7.62 & 0.05 & 0.97 & 0.34\\
Teaching (d) & 61 & 5 & 7.30 & 0.20 & 0.98 & 0.19 & 36 & 5 & 12.71 & 0.26 & 0.97 & 0.46 & 40 &5 & 3.17 & 0.67 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 3.70 & 0.45 & 0.98 & 0 & 36 & 3 & 5.89 & 0.12 & 0.97 & 0.28 & 41 & 3 & 4.42 & 0.22 & 0.98 & 0.18\\
Valued contributions (f) & 57 & 4 & 5.98 & 0.20 & 0.98 & 0.18 & 34 & 5 & 9.46 & 0.09 & 0.97 & 0.36 & 38 & 5 & 6.75 & 0.34 & 0.97 & 0.21 \\ \midrule
\multicolumn{16}{l}{\textbf{Racial/ethnic Identity}} \\ \midrule
Improvement of research (b)  & 59 & 3 & 0.97 & 0.81 & 0.98 & 0 & 34 &2 & 0.01 & 0.99 & 0.97 & 0 & 39 & 3 & 2.79 & 0.43 & 0.97 & 0 \\
Teaching (d) & 61 & 5 & 5.63 & 0.34 & 0.98 & 0.09 & 34 & 4 & 1.29 & 0.86 & 0.97 & 0 & 39 & 5 & 3.06 & 0.69 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 1.64 & 0.80 & 0.98 & 0 & 34 & 3 & 8.42 & 0.04 & 0.97 & 0.40 & 40 & 3 & 3.49 & 0.32 & 0.97 & 0.10 \\
Valued contributions (f) & 58 & 4 & 13.14 & 0.01 & 0.98 & 0.40 & 32 & 5 & 2.49 & 0.78 & 0.96 & 0 & 37 & 5 & 4.05 & 0.54 & 0.97 & 0 \\ 
\bottomrule
\end{tabularx}
   \begin{tablenotes}
      \item{Respondents to a post-event evaluation survey indicate their level of agreement on a six-point Likert-type scale to a range of statements (corresponding to Figure \ref{fig:survey}). Results are for hack weeks held in 2016 and 2017 for AHW and in 2016 for GHW and NHW, respectively. The number of respondents for each question is included in the table above. Additional figures showing the distributions of scores are available in the Supplementary Materials.}
      \item[\emph{a}]{The degrees of freedom for Cram\'{e}r's V corrected according to~\citep{bergsma2013}}
      \item[\emph{b}]{While the range of Likert items was the same for every question, the degrees of freedom for $\chi^2$ and Cram'{e}r's V may differ depending on the number of items with non-zero responses, and the number of non-zero items in the independent variable.}

@@

Given the broad diversity in skills and backgrounds of participants admitted to our hack weeks, a dependence of learning outcomes and teaching on career stage is plausible. At the same time, we put forth the hypothesis earlier in the this paper that peer learning is a major mode of knowledge transfer during hack weeks, and that this type of learning takes place at all career stages. However, we find no strong evidence for a significant difference between early-career researchers and senior participants for any of the three hack weeks for questions regarding learning outcomes of new tools and topics (a), improvements in day-to-day research (b) or overall improvements in science (c) (all statistical results are presented in Table \ref{tab:survey}). Only for GHW we find an indication that early-career researchers agree more strongly that the hack week improved their day-to-day research (p=0.02) with a large effect size of $\phi_c = 0.4$ (following~\citep{cohen1988}). 
Similarly, we find no strong indication that late-career researchers self-report a higher level of teaching at hack weeks compared to early-career researchers (d).
